---
title: "Hester-Dendy Discharge"
author: "CLB"
date: "9/9/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries
```{r message=FALSE}
library(tidyverse)
library(lubridate)
library(dataRetrieval)
library(scales)
library(ggthemes)
library(plotly)
library(ggpubr)
```
Site number is USGS gage number.

Orla 08412500
Iraan (Girvin) 08446500
Sheffield 08447000

```{r}
siteNumbers <- c("08412500", "08446500", "08447000")
```

Sets USGGS parameter code 00060 (discharge), 00065 (gage height), 00010 (temperature), etc.
for a full list of parameters visit: https://help.waterdata.usgs.gov/code/parameter_cd_query?fmt=rdb&inline=true&group_cd=%

not all parameters are available for all sites
```{r}
parameterCd <- c("00060", "00095") #discharge and gage height

#Days needed
startDate <- "2017-06-01"
endDate <- "2017-12-07"

#Get daily values from USGS
pecosQ <- readNWISdv(siteNumbers, parameterCd, startDate, endDate)

pecosQ <- renameNWISColumns(pecosQ)
#Convert CFS to CMS
pecosQ$Flow <- (pecosQ$Flow * 0.028316847)

```

Create Site column with site names based of of gage number and save to csv
```{r}
#Set site number as numeric, this is for ifelse below
pecosQ$site_no <- as.numeric(pecosQ$site_no)

pecosQ$Site <- ifelse(pecosQ$site_no == 08412500, "Orla",
                         ifelse(pecosQ$site_no == 08446500, "Iraan",
                          ifelse(pecosQ$site_no == 08447000, "Sheffield",
                              NA)))

pecosQ$Site<-factor(pecosQ$Site, levels = c("Orla", "Iraan", "Sheffield"), ordered=TRUE)

#write_csv(HD_Q, "~/Dropbox/HesterDendy/HD_Q.csv")
```


This is our 'master' template for time and date that we will want to fill in with data where the times do not exactly match even time intervals
```{r}
#Date and time sequence running every 15 minutes
summer_seq <- seq(as.POSIXct("2017-06-30", tz = "UTC"),
  as.POSIXct("2017-08-11", tz = "UTC"),
  by = ("1 day")
)

fall_seq <- seq(as.POSIXct("2017-10-10", tz = "UTC"),
  as.POSIXct("2017-12-05", tz = "UTC"),
  by = ("1 day")
)


# simply a data frame of date and time running the course of the data set
sampDates <- data.frame(summerDates = c(summer_seq, rep(NA, 57 - length(summer_seq))), fallDates =  fall_seq)
```

Sampling Dates
```{r}
startDate <- c("2017-06-30", "2017-10-10")
endDate <- c(as_date("2017-06-30") + days(42), as_date("2017-10-10") + days(56))
sampDates <- data.frame(startDate = startDate, endDate = endDate)
sampDates$startDate <- as_date(sampDates$startDate)
sampDates$endDate <- sampDates$startDate[1] + 42 
sampDates$endDate <- sampDates$startDate[2] + 56 
```

Daily Discharge CMS (Orig. fig in MS)
```{r}
pecosQplot <- ggplot(pecosQ, aes(Date, Flow))+
  geom_line(aes(linetype = Site)) +
  annotate("rect",
    xmin = as.Date("2017-06-30"), xmax = as.Date("2017-08-11"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  annotate("rect",
    xmin = as.Date("2017-10-10"), xmax = as.Date("2017-12-05"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14)) +
  labs(y = expression(Discharge~(m^3/s)), x = element_blank())+
  theme_classic()+
  theme(legend.title= element_blank(), axis.text = element_text(size = 10), axis.title = element_text(size = 12), legend.background = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank())+
  scale_linetype_manual(values=c("solid", "dashed", "dotted"))+
  scale_x_date(date_labels = "%b", breaks = "month")
  #facet_wrap(~Site, ncol=3, scales= "free")

#ggsave("Q.png", HD, device = NULL, "/Users/connor/Dropbox/Hester Dendy Project/", width = 6.5, height = 3.66, units = "in")
```
Manual Cond meas.
```{r}
spCond <- data.frame(Date = as.Date(c("2017-06-30", "2017-10-10", "2017-10-10")), Site = c("Orla", "Orla", "Iraan"), SpecCond = c(8403, 12135, 4648))
```


Working on new fig for MS after revisions
```{r}
ggplot(pecosQ, aes(Date, Flow))+
  geom_line(aes(linetype = Site)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14)) +
  labs(y = expression(Discharge~(m^3/s)), x = element_blank())+
  theme_clean()+
 # theme(legend.title= element_blank(), axis.text = element_text(size = 10), axis.title = element_text(size = 12), legend.position = c(0.835, 0.89), legend.background = element_blank())+
#  scale_linetype_manual(values=c("solid", "dashed", "dotted"))
  facet_wrap(~Site, scales= "free", ncol = 1)
#ggsave("Q.png", HD, device = NULL, "/Users/connor/Dropbox/Hester Dendy Project/", width = 6.5, height = 3.66, units = "in")

ggplot(pecosQ, aes(Date, SpecCond))+
  geom_line(aes(linetype = Site)) +
  annotate("rect",
    xmin = as.Date("2017-06-30"), xmax = as.Date("2017-08-11"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  annotate("rect",
    xmin = as.Date("2017-10-10"), xmax = as.Date("2017-12-05"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  labs(y = expression(~pecific~Conductivity~(mu*S/cm)), x = element_blank())+
  theme_classic()+
  theme(legend.title= element_blank(), axis.text = element_text(size = 10), axis.title = element_text(size = 12), legend.position = c(0.835, 0.89), legend.background = element_blank())+
  scale_linetype_manual(values=c("solid", "dashed", "dotted"))+
  scale_x_date(date_labels = "%b", breaks = "month")
#facet_wrap(~Site, ncol=3, scales= "free")


pecosCond <- ggplot(pecosQ, aes(Date, SpecCond))+
  geom_line(aes(linetype = Site)) +
  geom_point(data = spCond, aes(x = Date, y = SpecCond), shape = 8, size = 3)+
  geom_text(data = spCond, aes(x = Date, y = SpecCond, label = Site, hjust = -0.25))+
  annotate("rect",
    xmin = as.Date("2017-06-30"), xmax = as.Date("2017-08-11"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  annotate("rect",
    xmin = as.Date("2017-10-10"), xmax = as.Date("2017-12-05"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  labs(y = "Specific Conductivity\n(\u03BCS/cm)", x = element_blank())+
  theme_classic()+
  theme(legend.title= element_blank(), axis.text = element_text(size = 10), axis.title = element_text(size = 12), legend.position = c(0.835, 0.89), legend.background = element_blank())+
  scale_linetype_manual(values=c("solid", "dashed", "dotted"))+
  scale_x_date(date_labels = "%b", breaks = "month")
#facet_wrap(~Site, ncol=3, scales= "free")

New <- ggarrange(pecosQplot, pecosCond, ncol = 1, common.legend = T, legend = "top", align = "hv")
ggsave("NewFig.png", New, device = NULL, "/Users/connor/Dropbox/Hester Dendy Project/", width = 6.5, height = 3.66, units = "in")

```


Testing log scale
```{r}
ggplot(pecosQ, aes(Date, log(Flow)))+
  geom_line(aes(linetype = Site)) +
  annotate("rect",
    xmin = as.Date("2017-06-30"), xmax = as.Date("2017-08-11"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  annotate("rect",
    xmin = as.Date("2017-10-10"), xmax = as.Date("2017-12-05"), 
    ymin = -Inf, ymax = Inf,  fill = "black", alpha=.3)+
  labs(y = expression(Discharge~(m^3/s)), x = element_blank())+
  theme_classic()+
  theme(legend.title= element_blank(), axis.text = element_text(size = 10), axis.title = element_text(size = 12), legend.background = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank())+
  scale_linetype_manual(values=c("solid", "dashed", "dotted"))+
  scale_x_date(date_labels = "%b", breaks = "month")
```



